Individual and Differential Harm in Redistricting

### 2022-07-02 paper/paper.Rmd
update fig minis

# Motivation {#sec:motivation}

To motivate the concepts of individual and differential harm, we will make use of three examples, which are stylized representations of U.S. states: Mininois, Minissouri, and Minichusetts.
Mininois has one large Democratic city which can electorally dominate the rest of the state; Minissouri has two medium-sized cities which are not large enough to deliver a statewide Democratic majority; and Minichusetts has a uniform 3--2 Democratic split in every precinct.
Each example state has the same population and should be divided into 3 districts with population between 54 and 66.
Voters' preferences are assumed to be stable across elections, and turnout is 100%.
Schematics for these examples are shown in Figure \ref{fig:mini-schematic}(a)--(c).

>>>>

# Minivation {#sec:motivation}

To introduce and motivate the concepts of individual and differential harm, we will make use of Minissouri, a stylized representations of Missouri.
Minissouri has two medium-sized cities which are not large enough to deliver a statewide Democratic majority.
Minissouri has a population of 180 and should be divided into 3 districts with population between 54 and 66.
Voters' preferences are assumed to be stable across elections, and turnout is 100%.
A schematic for this example is shown in Figure \ref{fig:mini-schematic}.
